---
title: "Flourish Example"
embed-resources: true
filters:
  - flourish
---

## Heading

This filter adds the ability to specify in hashpipe comments instructions for highlighting the code in the rendered chunk.

By default, ordinary yellow highlighting is used:

```
#| flourish:
#| - target-rx: "[0-9]*"
```

```{r}
#| flourish:
#| - target-rx: "[0-9]*"

x <- 1:10
mean(x = 1:10)
```

It is also possible to specify custom formatting with the `style` tag.  Here you must provide the exact text that would appear in a CSS class definition.

```
#| flourish:
#| - target:
#|      - "mean"
#|      - style:
#|            - "background-color: #FFC0CB;"
```

```{r}
#| flourish:
#| - target:
#|      - "mean"
#|      - style:
#|            - "background-color: #FFC0CB;"

x <- 1:10
mean(x = 1:10)
```

One fun way to use this is to blank out code pieces for student exercises.

```
#| flourish:
#| - target:
#|     - "mean"
#|     - style: 
#|         - "color: transparent;"
#|         - "text-decoration: underline;"
```

```{r}
#| flourish:
#| - target:
#|     - "mean"
#|     - style: 
#|         - "color: transparent;"
#|         - "text-decoration: underline;"

x <- 1:10
mean(x = 1:10)
```



Note that blanking out pieces with `style` means the answers are still visible in the underlying HTML.  To fully replace the answers with placeholder space, use `mask`:

```{r}
#| flourish:
#| - target:
#|     - "mean"
#|     - mask: true
#|     - style: "text-decoration: underline;"

x <- 1:10
mean(x = 1:10)
```
